Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-10-04 analysis/output/figures/hypotheses/Hypotheses.Rmd
Updated filtering code

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 7)
}
```

>>>>

if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
   # filter(levels == str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief"))) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
    geom_vline(xintercept = 0, color = "white") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
    draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels), 
      covariates = factor(j, labels = covariate_labels)  
    ) %>%
    filter(
      levels ==   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
      covariates == c("Religion: Hindu", "Religion: Protestant", "Religion: Christian Orthodox", "Religion: Jewish")) %>% 
    ggplot(aes(x = Theta, y = covariates)) +
       geom_density_ridges(scale = 5, height = 3, rel_min_height = 0.01) +
       geom_vline(xintercept = 0, color = "white") +
       labs(y = "Covariates") +
       facet_wrap(~ levels, ncol = 5)
}
```

### 2019-10-04 manuscript/manuscript.Rmd
Updated filtering code

![Combined Results](output/figures/combined-results.png)

@@

![Relationship With Host Government](output/figures/relationship-with-gov.png)

@@

![Organizational Characteristics: Managerial Practices](output/figures/managerial-practices.png)

@@

![Organizational Characteristics: Funding Sources](output/figures/funding-sources.png)

@@

![Organizational Characteristics: Issue Areas](output/figures/issue-areas.png)

@@

![Organization](output/figures/organization.png)

@@

  ![](output/figures/demographics.png)

  - `Donation preferences ~ (Public affairs) + (Political ideology)`

>>>>

![](output/figures/combined-results.png)

@@

![](output/figures/relationship-with-gov.png)

@@

![](output/figures/managerial-practices.png)

@@

![](output/figures/funding-sources.png)

@@

![](output/figures/issue-areas.png)

@@

![](output/figures/organization.png)

@@

  ![](output/figures/demographics.png)
  - `Donation preferences ~ (Public affairs) + (Political ideology)`
